\documentclass[11pt,english]{article}

\usepackage{babel}
\usepackage[round]{natbib}
\usepackage{fullpage}

\title{Following the Leader and
Fast Rates in Linear Prediction:
Curved Constraint Sets and Other Regularities \\
\emph{Cover Letter}}
\author{Ruitong Huang \and Tor Lattimore \and Andr\'as Gy\"orgy \and Csaba Szepesv\'ari}


\begin{document}
\maketitle

We would like to submit our paper entitled "Following the Leader and
Fast Rates in Linear Prediction: Curved Constraint Sets and Other Regularities" for consideration to be published in the Journal of Machine Learning Research.

\begin{enumerate}
\item The manuscript is an extended version of our NIPS paper \citep{HuLaGySz16}, and it considers (natural) situations when the follow the leader algorithm performs well in online convex/linear optimization. Compared to the conference version, we have made several additions. In particular, we (i) included all the proofs, most importantly the full proof of the lower bound Theorem~6; (ii) added a new section (Section 4.1) on adaptive algorithms that have low regret in favorable situations and come with strong worst-case guarantees; (iii) provided experiments (Section 5); and (iv) explored in detail the connection between positive minimal principal curvature and strong convexity (Proposition~12).

\item We herby confirm that all authors are aware of the submission and provide consent to JMLR to review the submitted manuscript.

\item Possible conflicts of interests:
\begin{itemize}
\item Recent co-authors (with the year of the last joint publication): Shie Mannor, John Shawe-Taylor (2016), Koby Crammer (2015), Alexander Rakhlin (2014), G\'abor Lugosi (2012).
\item Co-workers: Russ Greiner (University of Alberta), Laurent Orseau, Nando de Freitas (future co-workers at Google DeepMind).
\end{itemize}

\item Suggested action editors:
Peter Auer, Mehryar Mohri, Yoram Singer.
\end{enumerate}
\bibliography{reference}
\bibliographystyle{plainnat}
\end{document}